---
title: "apply_family"
author: "Peter"
date: "March 29, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# apply function

apply(X, MARGIN, FUN)

- X being an array(2 dimensional array) or a matrix
- MARGIN = 1, 2 or c(1,2) with 1 - rows, 2 - columns (appling function on rows or columns or both)
- FUN - function used to apply on X

```{r}
x <- matrix(rnorm(30), ncol = 6, nrow = 5) # generate a random 5x6 matrix

apply(x, 2, sum)


```

# lapply function

lapply(X, FUN, additional arguments for FUN)
```{r}
 
x <- list("A" = c(1, 2, 3), "B" = c(4, 5, 6))

lapply(x, sum) # sum by interating over all entries in lists x


A <- matrix(rnorm(50), ncol = 10, nrow = 5)
x <- list("A" = data.frame(A))
lapply(x, sum) # if one of the entries in the lists is a data frame, it sums all the elements


# example of using the addtional argument
x <- list("A" = rnorm(10))
lapply(x, quantile, probs = c(0, 0.25, 0.75, 1)) 

```
``` {r}
A <- matrix(seq(1,9), ncol = 3)

B <- matrix(seq(10, 18), ncol = 3)

C <- matrix(seq(19, 27), ncol = 3)

MyList <- list(A, B, C)

# extract the second column of each matrix

lapply(MyList, "[", , 2)
```
The above `[`  is the selection operator which is from A[row, column]. The first parameter is for the rows, and we want all rows which left it empty.

For select all the record at (1, 2), we would do ```lapply(x, "[", 1, 2)```


# sapply function

It is another version of lapply which it will convert to the simpliest data type, usually vectot.

``` {r}
df <- read.csv("C:/Users\ZHou\Desktop\Tidy Data in Python\pew-raw.csv")
head(df)

```